Trends of SDR in Thessaloniki

### 2023-10-21 Article.Rmd
Commit 2023-10-21 11:12

@@

>>>>

<!-- ```{r szatrendsmonthly, echo = FALSE, fig.cap='*** Montlhly *** Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics("./images/SzaTrendsMonthly-1.png") -->
<!-- knitr::include_graphics("./images/SzaTrendsMonthly-4.png" ) -->
<!-- knitr::include_graphics("./images/SzaTrendsMonthly-7.png") -->
<!-- ``` -->

@@

<!-- ```{r echo = FALSE, fig.cap='*** Montly *** SDR trend ~ SZA', out.width='100%'} -->
<!-- knitr::include_graphics("./images/SzaTrendsSeasTogetherMonthly-2.png") -->
<!-- ``` -->
